---
title: "Higl level view of what R can do"
author: "Rupesh"
date: "26 January 2018"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
Here is a over view of how advanced vizualization can be done so simply using R
```{r}
library(ggplot2)
# loading the dependency
df <- read.csv("Mispriced-Diamonds.csv")
#loading the datasets
head(df)
```
now so you know what is there in data you can vizualize it using ggplot2

```{r}
p <- ggplot(df, aes(x = carat, y = price))
# loading the data layer and aestics layer
p + geom_point() -> q
# setting the geometry 
print(q)
```
above is the scatterplot for the data you can add colour and make it look clean
```{r}
p + geom_point(alpha = 0.2, aes(colour = clarity))
```
know that we have added colour to the data lets remove the oulires that are breaking the treand
```{r}
# for that we need to load the data once again to plot
p <- ggplot(df[df$carat < 3, ], aes(x = carat, y = price, colour = clarity))
print(p + geom_point(alpha = 0.1))
```

know we see the trend in our data lets fit some stats thow the data
```{r}
print(p + geom_point(alpha = 0.1) + geom_smooth())
```

so you can see that brown is the best clarity for a diamond over given price 

you can tell all the story using this simple vizualization without utterning a word

that how you can prdouce advanced plots with so simple code



thank you !
for more content on R visit <a href = "http://rpubs.com/Rupesh110" > Rupesh </a>

for more follow in my blog rupi.ml